\chapter*{Abstract}
This engineer's thesis is composed of two elements. The first element is
a computer game designed for computers running Linux OS. This work is
accompanied by a media that contains an executable file, which filename
extension is .love, which allows you to run the game. The second element is
a written part about the game.
Chapter 1 describes how to install the runtime environment LÖVE. After its
installation, the files with the extension .love will be treated by system as
executable files. Installation of LÖVE is required to run the game.
Chapter 2 discusses the controls within the game. The reader may find out how to
control the character, open screens containing information about inventory,
received and completed quests or unlocked skills. This chapter describes the
purpose of the game and explains in details how to battle with opponents.
Chapter 3 describes the components of the game. This chapter describes in
details all parts of the game. This chapter is not about the implementation
process, but it can rather be treated as a description of the final
effect. The reading of this section will enable the reader to understand the
goals that have been defined before the implementation process.
Chapter 4 lists and briefly describes the technologies used to achieve the
result described in the previous chapter. There are presented general
information about those technologies, as well as the reasons that led to
selecting them for use in the project.
Chapter 5 describes a mechanism of switching between the states of the game.
This is the one of the key elements used in the implementation of the game.
This chapter introduces the reader to the concept of game states, shows the
benefits of their use, lists what states were created in the process of
implementation of the game and describes what are the functions of each of
used game states.
Chapter 6 describes the logic of the game. In this chapter details related to
the implementation of the game are discussed. The reader can see which
directories and files were created. This chapter tells how the objectives
defined in chapter 3 have been achieved.
Chapter 7 summarizes the whole thesis. This is a brief summary of the most
important information discussed in previous chapters. Reader can read
what were the goals of thesis and what has been achieved. Also included are
the final conclusions and reflections that arise during the analysis of the
final result, which is a fully functional game.